Inference methods comparison for the simplified Naomi model

### 2023-02-21 src/naomi-simple_compare/comparison.Rmd
Ranked by worst nodes for TMB or adam as compared with each other

The following parameters have KS values greater than 0.5 in both dimensions.

```{r}
(big_ks <- ks_summary %>%
  filter(`KS(aghq, tmbstan)` + `KS(TMB, tmbstan)` > 0.5) %>%
  pull(Parameter))
```

>>>>

Want to create rank order lists of largest KS differences between methods:

```{r}
ks_comparison <- function(ks_summary, method1, method2, n) {
  ks_method1 <- paste0("KS(", method1, ", tmbstan)")
  ks_method2 <- paste0("KS(", method2, ", tmbstan)")
  ks_summary[["KS difference"]] <- ks_summary[[ks_method1]] - ks_summary[[ks_method2]]
  ks_summary %>%
    filter(Type != "Hyper") %>%
    arrange(desc(`KS difference`)) %>%
    head(n = n)
}
```

Nodes where `TMB` beats `adam`:

```{r}
ks_comparison(ks_summary, method1 = "adam", method2 = "TMB", 10)
```

Nodes where `adam` beats `TMB`:

```{r}
ks_comparison(ks_summary, method1 = "TMB", method2 = "adam", 10)  
```
